Metrics

### 2023-12-07 src/plots.Rmd
Fix plots script

```{r}
df <- df %>% mutate(
    "age_range" = str_replace(
        na.omit(age_range),
        "\\s*\\(.*\\)",
        ""
    ))
```

@@

```{r}
df <- raw_df %>%
    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))
```

>>>>

```{r}
df <- raw_df %>% mutate(
    "age_range" = str_replace(
        age_range,
        "\\s*\\(.*\\)",
        ""
    ))
```

@@

```{r}
df <- df %>%
    filter(!is.na(physician_cghr10) & !is.null(physician_cghr10))
```
